\documentclass{article}
\usepackage[utf8]{inputenc}

\title{A Comparative Study Of Brain Computer Interface Algorithms: SVM Classifiers vs Neural Networks}
\author{Krishna Vijay Samayamantri}
\date{November 2018}

\begin{document}

\maketitle

\section{Acknowledgements}
I would like to thank my parents and brother for supporting me throughout these three years in every possible way. Mom, you made sure that I do not feel homesick at all by talking with me every single day, twice a day for hours. I could share my fears, pain, sorrows and joys with you. Dad, no matter how mad I was at you, and how much I have insulted you, you brushed it aside and supported me. You gave me valuable insights in research techniques and writing. Brother, you have been a backbone to me. Many times, I could just talk to you and get the right answer to help me overcome the obstacle in front of me. You challenged me when I was being lazy, you reassured me when I was freaking out, you have inspired me through your own research work. Dad and Kutte, you guys have sent me money many times upon short notice. Without you three, I would not have been able to complete my thesis and my degree.

I am highly grateful to Dr. Deborah Won, my thesis guide. I have met you on my first day at school and you patiently listened to all my thesis ideas, no matter how far-fetched they were. I was not a good research student, but you have showed enormous patience despite my constant shenanigans and failures, and guided me at every step of my thesis. From the first idea I started working, my research topic changed multiple times. You have figured out what was needed for me at every step and provided me with appropriate support, including a hardworking team.

I thank my entire team. Without you I would not have been able to complete my research in time. Diego, man, you are the ultimate doer. I have learned a lot from you. With you hard-work and dedication, you got the whole project rolling by providing the project with a dedicated laptop, a robotic arm and all the tech support required. You have built the Labview interface along with Antonio and Ellie. You got the Emotiv PRO and Cortex installed and running. Diego, thank you very much. 

Antonio, you were another important person without whom the BCI project would not be possible. You, along with Aldo, did the preliminary data collection, pre-processing and laid out the trends that can be used in developing the BCI algorithm. Also, you were the one who figured out the markers and their synchronization. Antonio and Aldo, thank you very much. 

Ellie, despite being tied up with your own stuff, you have helped in getting the data collection with synchronized markers working. Thank you Ellie.

Brian, you asked me a lot of questions and nudged me in the right direction regarding algorithm development. Peter, you have helped me in cracking the artifact removal code and the Choi paper that set the wheels rolling for my thesis.

Ashar and Nicholas, you guys have helped me develop the data preparation code and data analysis. Thank you very much. 

Kenji, you have helped me with creation of the final Labview code to collect synchronized data. Thank you very much.

I wish to thank Dr. Raj Pamula for recommending me to Cal State LA and giving me this opportunity to work with many accomplished people. I wish to thank Dr.~Fereydoun Daneshgaran, Dr~ Marina Mondin, Dr.~Saeid Barzegarjalali and Dr.~Shaurya Agarwal for teaching and supporting me.

I also wish to thank the guys at BMES lounge/NETLab, for supporting me during my time here. Patrick, Amadeo, Amit, James, Luis, Albert, thanks for the good times.
I wish to thank my study buddies: Sneha, Sunitha, Ismail, Alex, Sreelekha, Romit, Pragnesh, Freddy. Thanks for being there for me.

\end{document}
