\documentclass{article}
\usepackage[utf8]{inputenc}

\title{A Comparative Study Of Brain Computer Interface Algorithms: SVM Classifiers vs Neural Networks}
\author{Krishna Vijay Samayamantri}
\date{November 2018}

\begin{document}

\maketitle

\section{Contents/Outline}
This is the Outline of the BCI Thesis. This file lists all the chapters that are contained in the thesis.
\begin{enumerate}
    \item Introduction: BCI for Self Locomotion
    \begin{itemize}
        \item Discuss about BCI Survey paper
        \item Add BCI Flowchart/Block Diagram
        \item Scope and Outline of the Present Work
    \end{itemize}
    \item Data Collection
    \begin{itemize}
        \item Hardware Setup 
        \begin{enumerate}
            \item Emotiv headset 
            \item Experiment details
        \end{enumerate}
        \item Software Setup 
        \begin{enumerate}
            \item Labview Code
            \item Emotiv Software
        \end{enumerate}
        \item Physionet Dataset
        \begin{enumerate}
            \item Preliminary Data Analysis
            \item Labelled Data Points
        \end{enumerate}
    \end{itemize}
    \item General Outline of BCI Algorithm
    \newline (Add Block Diagram of BCI Algorithm)
    \begin{itemize}
        \item Artifact Removal
        \begin{enumerate}
            \item Write about Artifact Removal Survey Paper?
        \end{enumerate}
        \item Data Preparation
        \begin{enumerate}
            \item Generate ERP's
            \item Label Data Snippet with Marker labels to check accuracy of classification
        \end{enumerate}
        \item Feature Extraction
        \item Classification Algorithms
        \begin{enumerate}
            \item Support Vector Machines (SVM)
            \item Neural Networks
        \end{enumerate}
    \end{itemize}
    \item Choi et al. (Chosen SVM Algorithm)
    \begin{enumerate}
        \item Difference between Choi and Ramoser
    \end{enumerate}
    \item Barbosa et al. (Chosen ANN Algorithm)
    
    \item Results and Discussion
    \item Conclusion and Future Works
    \item References
\end{enumerate}

% Add Questions here

\section{Questions}
\begin{itemize}
    \item Should I add the parts of Data Collection using Emotiv, as only 1 data file is collected using the Labview-Emotiv Setup?
    \item Should I write about the Artifact Removal Survey Paper?
    \item For the Neural Network based algorithm, I have chosen Barbosa et al over the other available paper Craig et al, as Barbosa have a better description of the ANN algorithm(s) used. Barbosa have also applied multiple ANN methods for classification and compared their performance.
\end{itemize}

\end{document}